State and Parameter Estimation for Spatio-Temporal Neural Fields

### 2010-05-09 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
added a conclusion draft

\omg{DISCUSS SHORT-COMINGS AND FUTURE WORK}
In this paper the widths of the connectivity kernel basis functions are assumed to be known. In a future work we plan to extend this work to unknown widths. We hope to achieve this by using a sufficiently large set of connectivity basis functions within the physiological plausible limits, and letting estimation procedure take care of the weights. In addition, the assumption homogeneity can be relaxed, where heterogeneity can be modelled by careful placement of field basis functions. For example, if cortical regions have a greater density of neural populations, then more basis functions can be used in these areas. In this scenario, model selection and basis function positioning can be achieved using instantaneous frequency analysis of the the neural field or alternative model selection tools based on information criteria.

@@

\section{Conclusion}\label{ConclusionSection}

>>>>

\omg{DISCUSS SHORT-COMINGS AND FUTURE WORK}
In this paper the widths of the connectivity kernel basis functions are assumed to be known. In a future work we plan to extend this work to unknown widths. We hope to achieve this by using a sufficiently large set of connectivity basis functions within the physiological plausible limits, and letting estimation procedure take care of the weights. In addition, we plan to show in future work how the assumption homogeneity can be relaxed, where heterogeneity can be modelled by careful placement of field basis functions. For example, if cortical regions have a greater density of neural populations, then more basis functions can be used in these areas. In this scenario, model selection and basis function positioning can be achieved using instantaneous frequency analysis of the the neural field or alternative model selection tools based on information criteria. This is a topic for future research. Future work should also be targeted to include a more realistic synaptic response kernel, with finite rise and decay times and finite propagation times into the neural field equations.

@@

\section{Conclusion}\label{ConclusionSection}
This paper presented a novel model-based framework for patient-specific state and parameter estimation of neural fields. This framework enables a fundamental link between patient-specific physiologic data and theoretical neural field models. This link has the potential to lead to advances in our basic understanding of the dynamics of the brain at the macro/mesoscopic scale. Forming a greater understanding neural dynamics at this scale may lead to new and improved treatment options for diseases such as epilepsy.
